\subsection{Features}

% % pezzo su come sono fatte stringhe


In this work we want to find \emph{primitive} features, resembling the possible types of strokes used to write a word, to characterize the sample from which they are extracted in order to perform clustering on their set.

The features are identified by the study of a sub-portion, or window, of the images extracted by the paper on which this work is based.

The features are located through a study of an area, the window, to which they are implicitly associated: as such there is no clear order of which of the features found in the area comes first.
Due to the absence of such \emph{native} order the string that defines a window is maintained consistent with the other strings trough the convention of generating the string with the features' identifiers always taking the same order, if present.

The chosen way to resolve the issue however presents the problem of making sliding windows inapplicable: this means that a sample must necessarily be cut in separate windows, which are allowed to overlap, with the corresponding effect that due to the random cut some features like \textit{loops} may not be recognised in an instance and recognised in another. 

\paragraph{Windows}

Currently we have chosen to cut the samples in windows of 32 pixels each with the exception of the last part of the sample that, deemed irrelevant to the end of characterization due to containing almost always white space, is simply ignored.

These windows are spaced only 16 pixels from the preceding and succeeding one, with the intent of creating overlap and lengthening the string that characterizes the samples.

While the simplest way to create the windows is simply creating a new PIX with the required coordinates it requires unnecessary passages and time in the creation of new objects. We have thus preferred to increase the complexity of the functions that search for the features, to whom we pass as a variable the original sample PIX with information about the \textit{offset} at which to start the search and the \textit{width} of the window.

% %parte su diversa width diverse feature

\subsubsection{Whitespace}  

The first feature that is search in the windows is the white space. This way if a window is identified as blank will not be necessary to proceed with the investigation of other features, saving time.

A window is identified as blank if the average pixel values is below a preset white threshold.

\subsubsection{Loop}

The feature that represents a loop is recognized only with maximum window size.
To locate a loop is initially found a black pixel. The idea behind is to imagine that we had found a point on the border and meet two transitions going in the same direction, first from black to white then from white to black. Between the two transitions there must be a minimum step above a preset threshold where the pixels are white.

If the above condition occurs then we verify that it is real in the same way along the horizontal axis. We then sit in the center of the loop (the median value of the segment described above) and check that, moving both right or left you get a transition from white to black after a suitable number of white pixels.

The implemented method has numerous problems related mainly to the identification of the center of the loop in the segment. With a value of threshold too high also might have to discard some loops too small. The method also does not take into account the thickness of the stroke.
However, with appropriate threshold values you can get good results and to identify obvious loops of various segments.

\subsubsection{Dot}

To find the points in the segment we proceed as in the previous case, seeking a first black pixel.

At that point, for it to be a Dot, there must be a circle of a given radius (whose value is preset and adjustable) in which the pixels are black and outside of that, for some white space.

Even in this case you have the problem of determining a good value of the radius of the circle, having to remember even the size of the stroke.

\subsubsection{Diagonal line}

The feature representing a diagonal line, both upward and downward facing, is extracted through a simple exhaustive scansion of the window for lines of connected black pixels that have an incline in a range of values and are sufficiently long.

At the moment the function doesn't account for the width of the lines found, thus diagonal features can be recognised in a shapeless blob of black pixel that is sufficiently big. 
   
There's a distinction for diagonal features that appear in the lower and upper bottom of the window.
At most in a window the function identifies a couple of upward and a couple of downward facing lines (lower and upper parts), once one has been found it stops searching for the same type.

\subsubsection{Cross}
The function, having found at most a lower and upper case for upward and downward diagonal lines, proceeds to confront the edge points of these lines: if they possibly intersects it extracts a \emph{crossing} feature with distinction if the crossing happens in the lower or upper part of the window. 

The problems with this sub-feature are that intersections of bottom and upper lines of the same type (e.g. both upward facing) with different inclines are not recognised, in the same way there's no consideration for intersections made from lines that are not the "primary" bottom and upper diagonals: if in a single windows are present more lower upwards diagonals and one of them other than the first intersects the recognised downward diagonal, such a crossing is ignored.

The crossing feature may also not necessarily be a complete intersection, in fact for recognition there just needs to be a merging of a downward and upward line. 


\subsubsection{Horizontal and Vertical line}
Both horizontal and vertical lines' features are extracted through
a simple scan of the window.
The horizontal lines requires a double-window for their implicit characteristic.
The function identifies a line if it finds a connected row or column of black pixels that has sufficient length, in particular it distinguishes the lines found in normal or long through an ulterior threshold.
Once a fitting line has been found the function keeps searching for more, continuing the scansion of the window after having moved a certain distance from the last line found in order not to confuse a particularly thick stroke as different separate lines.
There still persists the problem that the stroke width is not fully considered so a big blob of black pixels is seen as a series of horizontal and vertical lines, at the same time such an occurrence is rare so the presence of many horizontal and vertical lines ends up distinguishing the word in itself.     
